Ecosystem carbon balance in the Hawaiian Islands under different scenarios of future climate and land use change

### 2020-11-16 Manuscript/HI_Model_ms.Rmd
updated manuscript files

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis [@friedlingstein_global_2019].

>>>>

## Introduction
Terrestrial ecosystems are a major sink for atmospheric carbon dioxide (CO~2~), removing ~30% of human emissions on an annual basis [@friedlingstein_global_2019]. However, there is a high degree of uncertainty surrounding the strength of the land carbon sink because of its sensitivity to annual variability in climate and human land use and land cover change [@ahlstrom_dominant_2015; @prestele_current_2017]. These climate and land-use driven uncertainties are so high that annual estimates of carbon sequestration by terrestrial ecosystems are often estimated indirectly by subtracting annual atmospheric and ocean carbon sink estimates from annual human CO~2~ emissions [@le_quere_global_2013; @friedlingstein_global_2019].
